Extended Formal Analysis of the EDHOC Protocol in Tamarin

### 2022-07-23 paper.tex
Final version

\input{macros}

\begin{document}
\title{Extended Formal Analysis of the EDHOC Protocol in Tamarin}
\author{
    Karl Norrman\inst{1,2}\orcidID{0000-0003-0164-1478} \and
    Vaishnavi Sundararajan\inst{3} \and
    Alessandro Bruni\inst{4}
}
\authorrunning{Norrman, Sundararajan and Bruni}
\institute{
    KTH Royal Institute of Technology, Stockholm, Sweden \and
    Ericsson Research, Security, Stockholm, Sweden\\
    \email{karl.norrman@ericsson.com} \and
    University of California Santa Cruz, USA\\
    \email{vasundar@ucsc.edu} \and
    IT University of Copenhagen, Copenhagen, Denmark\\
    \email{brun@itu.dk}
}

@@

%-------------------------------------------------------------------------- sub
\subsection{\mTamarin{}}
\label{sec:tamarin}
We extend the formal \mEdhoc{} model of~\cite{Norr21}, using the tool \mTamarin{}~\cite{DBLP:conf/cav/MeierSCB13}, which is an 
interactive
tool for the symbolic verification of security protocols.
%
Protocols are modelled in \mTamarin{} as multiset rewrite rules which encode 
a
transition relation.
%
The elements of these multisets, called facts, contribute to the global
system state.
%
For syntactic sugar, \mTamarin{} also allows the use of let-bindings and tuples.
%
For ease of presentation, we will present the model and properties in a
slightly different syntax in this paper, but this syntax can be directly
mapped to that of \mTamarin.
%

@@

\begin{figure*}[ht]
\begin{align*}
    \mPredPcs \triangleq\ & \forall \mTID, I, R, \mSessKey, t_2, t_3\mLogicDot
    \mK^{t_3}(\mSessKey)\  \land\ 
    (\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, 
\mRComplete^{t_2}(\mTID, 
I, R, 
\mSessKey))
    \rightarrow\\
    &(\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)
    \ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(R, \mSessKey))
    \ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(I, \mSessKey))\\
	&\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID, I, R) \land 
\mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID, I, R) 
\land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[1em]
%    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID, R, \mSessKey, S) 
%\land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_2\mLogicDot \mIComplete^{t_2}(I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_R, t_1\mLogicDot \mRStart^{t_1}(\mTID_R, R, \mSessKey, 
S) \land t_1 \lessdot t_2
    \land (\forall \mTID_I', I', R', t_1' \mLogicDot \mIComplete^{t_1'}(\mTID_I', 
I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land 
\mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[1em]
%
    \mPredInjR \triangleq\ &
    \forall \mTID_R, I, R, \mSessKey, S, t_2\mLogicDot 
\mRComplete^{t_2}(\mTID_R, 
I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_I, t_1\mLogicDot \mIStart^{t_1}(\mTID_I, I, R, \mSessKey, 
S) \land t_1 \lessdot t_2
    \land (\forall \mTID_R', I' R' t_1' \mLogicDot 
\mRComplete^{t_1'}(\mTID_R', 
I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID_R, R, 
\mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot 
t_2))\\[1em]
%
    \mPredImpI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_1\mLogicDot 
\mIComplete^{t_1}(\mTID_I, 
I, R, \mSessKey, 
S)
    \rightarrow\\
      &(\forall \mTID_R, I', R', S', t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, 
I', R', \mSessKey, S') \rightarrow
             (I=I' \land R=R' \land S=S')\\
      &\ \land (\forall \mTID_I', I', R', S', t_1'\mLogicDot
        \mIComplete^{t_1'}(\mTID_I', I', R', \mSessKey, S') \rightarrow t_1' \doteq 
t_1
        ))\\
    &\lor(\exists t_0\mLogicDot \mRevLTK^{t_0}(R) \land t_0 \lessdot t_1)
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey))\\
    &\lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land 
\mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))
\end{align*}
%
\caption{Formalization of security properties and adversary model.}
\label{fig:props}
\end{figure*}

@@

In the \mIComplete{} event, \mTID{} represents a ``thread identifier'' which uniquely identifies the
current session, $I$ represents the identity of the initiator,
and $R$ represents the identity of the party who the initiator believes is
playing the responder role, while \mSessKey{} stands for the established
session-key material.
%
\mRComplete{} has analogous parameters; in particular, the responder $R$
believes $I$ is the party playing the initiator role.
%
Intuitively, the PCS property states that an adversary obtains \mSessKey{}
only if one of the following conditions hold: either a party's long-term key
is compromised before their run ends, or \mSessKey{} is directly revealed to
the attacker, or the TEE interface for the responder is used during the current
session for the initiator, i.e., after the initiator starts and before it
completes, or, similarly, the TEE interface for the initiator is used during the
current session for the responder.
%
Note that the properties in Figure~\ref{fig:props} are unlike the actual \mTamarin{} lemma in one minor way: \mTamarin's logic does not allow disjunctions to appear on
the left-hand side of an implication inside a universally-quantified formula.
%
Therefore, in the \mTamarin{} code, instead of using the disjunction
$\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\,
\mRComplete^{t_2}(\mTID, I, R, \mSessKey)$
to model the fact that either party may have completed their execution, we use
a single action parametrized by the terms $\mTID$, $I$, $R$, and \mSessKey.

@@

%---------------------------------------------------------------------------sub
\subsection{Encoding \mEdhoc{} in \mTamarin{}}
\label{sec:modeling}
%
In this section, we describe how we model the \mSigSig, \mSigStat, \mStatSig,
and \mStatStat{} methods of \mEdhoc{} in \mTamarin.
%
As in~\cite{Norr21}, we construct the \mTamarin{} model by utilizing the fact
that all methods of \mEdhoc{} share a common underlying structure
(as shown in Figure~\ref{fig:edhocFramework}).
%
We do so by using a single specification file in the M4 macro language,
which generates all the methods.
%
As in~\cite{Norr21}, we only present the \mStatSig{} method which illustrates
the use of two different authentication methods.
%
The full \mTamarin{} code for all models can be found 
at~\cite{edhocTamarinRepo}.
%

@@

\begin{scriptsize}
\begin{verbatim}
1 lemma secrecyPFS:
2    all-traces
3    "All u v sk tid #t3 #t2.
4       (K(sk)@t3 & CompletedRun(u, v, sk, tid)@t2) ==>
5       ( (Ex #t1. LTKRev(u)@t1 & #t1 < #t2)
6       | (Ex #t1. LTKRev(v)@t1 & #t1 < #t2)
7       | (Ex #t1. EphKeyRev(sk)@t1)
8       | (Ex m1 #t0 #k. I1(tid, u, v, m1)@t0 & TEE(v)@k & (t0 < k | k < t2))
9       | (Ex m1 m2 #t0 #k. R2(tid, v, m1, m2)@t0 & TEE(u)@k & (t0 < k | k < t2))
10    )"
\end{verbatim}
\end{scriptsize}
%

In this formalization, we use the action \mT{CompletedRun(u, v, sk)}
(in line 4) to represent the disjunction of the events $\mIComplete^{t_{2}}$
and $\mRComplete^{t_{2}}$.
%
As expected, this action is emitted by both \mT{I3} and \mT{R4}.
%
Similarly, the action \mT{EphKeyRev(sk)} in line 7 stands for the reveal of
the ephemeral key for $I$ or $R$ or both.
%
Lines 8 and 9 captures that the parties TEEs must be inaccessible to the
adversary between the start and end of the execution as seen by each party
respectively.
%

>>>>

%\input{macros}
\usepackage{ifthen}
\newcommand{\mPoint}[1]{{\color{red}\textbf{Point: }#1}}
\newcommand{\mcneed}{\textbf{Citation needed}}
\newcommand{\mcfix}{\textbf{Fix citation}}

\definecolor{cbnavy}{RGB}{15, 32, 128}
\definecolor{cborange}{RGB}{245, 121, 58}
\definecolor{cbgreen}{RGB}{0, 150, 50}

%\newcommand{\runhead}[1]{\noindent\textbf{#1. }}
\newcommand{\runhead}[1]{\subsubsection{#1}}

% -- Fonts and styles for names
%\newcommand{\mItemStyle}[1]{\ensuremath{#1}}
%\newcommand{\mSetStyle}[1]{\ensuremath{\mathrm{\mathbf{#1}}}}
%\newcommand{\mFunStyle}[1]{\text{\textup{\textsf{#1}}}}
%\newcommand{\mConstStyle}[1]{\text{\textup{\textsf{#1}}}}
%\newcommand{\mVarStyle}[1]{\mathit{#1}}
%\newcommand{\mFactStyle}[1]{\text{\textsf{#1}}}
%\newcommand{\mMethodStyle}[1]{\mbox{\mConstStyle{#1}}}
%\newcommand{\mProtocolStyle}[1]{\mbox{\textrm{#1}}}

%\newcommand{\mItemStyle}[1]{\ensuremath{#1}}
%\newcommand{\mSetStyle}[1]{\ensuremath{\mathrm{\mathbf{#1}}}}
\newcommand{\mFunStyle}[1]{\textsf{#1}}
\newcommand{\mConstStyle}[1]{\textsf{#1}}
\newcommand{\mVarStyle}[1]{\mathit{#1}}
\newcommand{\mFactStyle}[1]{\textsf{#1}}
\newcommand{\mMethodStyle}[1]{\mConstStyle{#1}}
\newcommand{\mProtocolStyle}[1]{\text{#1}}

% -- Macros for consistent wording
\newcommand{\mSpec}{specification}  % The EDHOC spec document we are analyzing
\newcommand{\mDate}{2020-07-06}

% -- Formalization notation
\newcommand{\mRevLTK}{\ensuremath{\mathbf{A}_\mFunStyle{LTK}}}
\newcommand{\mTEE}{\ensuremath{\mathbf{A}_\mFunStyle{TEE}}}
\newcommand{\mRevEph}{\ensuremath{\mathbf{A}_\mFunStyle{Eph}}}
\newcommand{\mIStart}{\ensuremath{\mathbf{I}_\mFunStyle{S}}}
\newcommand{\mIComplete}{\ensuremath{\mathbf{I}_\mFunStyle{C}}}
\newcommand{\mRStart}{\ensuremath{\mathbf{R}_\mFunStyle{S}}}
\newcommand{\mRComplete}{\ensuremath{\mathbf{R}_\mFunStyle{C}}}
\newcommand{\mISend}{\ensuremath{\mathbf{I}_{\mFunStyle{SEND}}}}
\newcommand{\mRRecv}{\ensuremath{\mathbf{R}_{\mFunStyle{Recv}}}}

\newcommand{\mPredPcs}{\ensuremath{\mathbf{PCS}}}
\newcommand{\mPredInjI}{\ensuremath{\mathbf{InjAgree}_I}}
\newcommand{\mPredInjR}{\ensuremath{\mathbf{InjAgree}_R}}
\newcommand{\mPredImpI}{\ensuremath{\mathbf{ImpAgree}_I}}
\newcommand{\mPredImpR}{\ensuremath{\mathbf{ImpAgree}_R}}
\newcommand{\mSecADthree}{\ensuremath{\mathbf{{Sec}\mADthree}}}
\newcommand{\mIntADthree}{\ensuremath{\mathbf{Integ\mADthree}}}
\newcommand{\mK}{\ensuremath{\mathcal{K}}}
\DeclareMathOperator{\mLogicDot}{.}

% -- Domain specific macros
\newcommand{\mArxiv}{\texttt{arXiv}}
\newcommand{\mTamarin}{\mProtocolStyle{Tamarin}}
\newcommand{\mProverif}{\mProtocolStyle{ProVerif}}
\newcommand{\mEdhoc}{\mProtocolStyle{EDHOC}}
\newcommand{\mMuEdhoc}{\mProtocolStyle{\ensuremath{\mu}EDHOC}}
\newcommand{\mOscore}{\mProtocolStyle{OSCORE}}
\newcommand{\mSigma}{\mProtocolStyle{SIGMA}}
\newcommand{\mSigmaI}{\mProtocolStyle{SIGMA\nobreakdash-I}}
\newcommand{\mCbor}{\mProtocolStyle{CBOR}}
\newcommand{\mCose}{\mProtocolStyle{COSE}}
\newcommand{\mCoseEncrypt}{\mProtocolStyle{COSE\_Encrypt0}}
\newcommand{\mCoseSign}{\mProtocolStyle{Cose\_Sign1}}
\newcommand{\mHkdf}{\mProtocolStyle{HKDF}}
\newcommand{\mHkdfExtract}{\mProtocolStyle{HKDF\nobreakdash-extract}}
\newcommand{\mHkdfExpand}{\mProtocolStyle{HKDF\nobreakdash-expand}}
\newcommand{\mHmac}{\mProtocolStyle{HMAC}}
\newcommand{\mAead}{\mProtocolStyle{AEAD}}
\newcommand{\mAeadDecrypt}{\mProtocolStyle{AEAD\nobreakdash-decrypt}}
\newcommand{\mDecrypt}{\mProtocolStyle{decrypt}}
\newcommand{\mOptls}{\mProtocolStyle{OPTLS}}
\newcommand{\mNoise}{\mProtocolStyle{Noise}}
\newcommand{\mTls}{\mProtocolStyle{TLS}}
\newcommand{\mDandTls}{\mProtocolStyle{(D)TLS}}
\newcommand{\mCtls}{\mProtocolStyle{cTLS}}
\newcommand{\mCoap}{\mProtocolStyle{CoAP}}

\newcommand{\mStat}{\mMethodStyle{STAT}}
\newcommand{\mSig}{\mMethodStyle{SIG}}
\newcommand{\mPsk}{\mMethodStyle{PSK}}
\newcommand{\mStatStat}{\mMethodStyle{STAT-STAT}}
\newcommand{\mStatSig}{\mMethodStyle{STAT-SIG}}
\newcommand{\mSigStat}{\mMethodStyle{SIG-STAT}}
\newcommand{\mSigSig}{\mMethodStyle{SIG-SIG}}
\newcommand{\mPskPsk}{\mMethodStyle{PSK-PSK}}

\newcommand{\mSid}{\mConstStyle{sid}}    % session id = (u, v, s-key)

\newcommand{\mXor}{\mConstStyle{XOR}}
\newcommand{\mSuites}{\ensuremath{S_I}}
\newcommand{\mMethod}{\ensuremath{M}}
\newcommand{\mCi}{\ensuremath{C_I}}
\newcommand{\mCr}{\ensuremath{C_R}}
\newcommand{\mGu}{\ensuremath{Q_{s,U}}}
\newcommand{\mGi}{\ensuremath{Q_{s,I}}}
\newcommand{\mGr}{\ensuremath{Q_{s,R}}}
\newcommand{\mPriv}[1]{\ensuremath{d_{s,#1}}}
\newcommand{\mPub}[1]{\ensuremath{Q_{s,#1}}}
\newcommand{\mPrivE}[1]{\ensuremath{d_{e,#1}}}
\newcommand{\mPubE}[1]{\ensuremath{Q_{e,#1}}}
\newcommand{\mX}{\ensuremath{d_{e,I}}}
\newcommand{\mY}{\ensuremath{d_{e,R}}}
\newcommand{\mGiy}{\ensuremath{\mY\cdot\mGi}}
\newcommand{\mGrx}{\ensuremath{\mX\cdot\mGr}}
\newcommand{\mGx}{\ensuremath{Q_{e,I}}}
\newcommand{\mGy}{\ensuremath{Q_{e,R}}}
\newcommand{\mGxy}{\ensuremath{P_e}}
\newcommand{\mSessKey}{\ensuremath{Z}}
\newcommand{\mIDPsk}{\mConstStyle{ID\_PSK}}
\newcommand{\mSign}[1]{\ensuremath{\mathit{sign_{#1}}}}
\newcommand{\mVf}[1]{\ensuremath{\mathit{vf_{#1}}}}
\newcommand{\mDH}{\ensuremath{\mathit{dh}}}
\newcommand{\mTH}{\ensuremath{\mathit{th}}}
\newcommand{\mTHtwo}{\ensuremath{\mathit{th}_2}}
\newcommand{\mKtwoe}{\ensuremath{K_\mathit{2e}}}
\newcommand{\mKtwom}{\ensuremath{K_\mathit{2m}}}
\newcommand{\mKtwoae}{\ensuremath{K_\mathit{2ae}}}
\newcommand{\mTID}{\ensuremath{\mathit{tid}}}

\newcommand{\mKthreeae}{\ensuremath{K_\mathit{3ae}}}
\newcommand{\mKthreem}{\ensuremath{K_\mathit{3m}}}

\newcommand{\mTHthree}{\ensuremath{\mathit{th}_3}}
\newcommand{\mhplain}{\ensuremath{h''}}
\newcommand{\mCredi}{\ensuremath{Q_{s,I}}}
\newcommand{\mCredr}{\ensuremath{Q_{s,R}}}
\newcommand{\mHash}{\ensuremath{h}}

\newcommand{\mTHfour}{\ensuremath{\mathit{th}_4}}
\newcommand{\mAuthi}{\ensuremath{\mathit{Auth}_I}}
\newcommand{\mAuthr}{\ensuremath{\mathit{Auth}_R}}

\newcommand{\mMactwo}{\ensuremath{\mathit{MAC}_2}}
\newcommand{\mMacthree}{\ensuremath{\mathit{MAC}_3}}

\newcommand{\mSigtwo}{\ensuremath{\mathit{Sig}_2}}
\newcommand{\mSigthree}{\ensuremath{\mathit{Sig}_3}}

% \newcommand{\mMsgone}{\mConstStyle{m1}}
% \newcommand{\mMsgtwo}{\mConstStyle{m2}}
% \newcommand{\mMsgthree}{\mConstStyle{m3}}
\newcommand{\mMsgone}{\ensuremath{m_1}}
\newcommand{\mMsgtwo}{\ensuremath{m_2}}
\newcommand{\mMsgthree}{\ensuremath{m_3}}

\newcommand{\mCipher}{\mConstStyle{CIPHERTEXT\_2}}

\newcommand{\mAD}{\ensuremath{\mathit{ad}}}
\newcommand{\mADone}{\ensuremath{\mathit{ad}_1}}
\newcommand{\mADtwo}{\ensuremath{\mathit{ad}_2}}
\newcommand{\mADthree}{\ensuremath{\mathit{ad}_3}}

\newcommand{\mPRK}{\ensuremath{\mathit{PRK}}}
\newcommand{\mPRKtwo}{\ensuremath{\mPRK_\mathit{2e}}}
\newcommand{\mPRKthree}{\ensuremath{\mPRK_\mathit{3e2m}}}
\newcommand{\mPRKfour}{\ensuremath{\mPRK_\mathit{4x3m}}}

\newcommand{\mIdcredi}{\ensuremath{ID_I}}
\newcommand{\mIdcredr}{\ensuremath{ID_R}}
\newcommand{\mLtki}{\mConstStyle{ltk\_I}}
\newcommand{\mLtkr}{\mConstStyle{ltk\_R}}
\newcommand{\mLtk}{\mConstStyle{ltk}}

\newcommand{\cm}{\checkmark}

% TIKZ messages and actions
\newcommand{\msg}[4]{\draw[->,thick] ([yshift=-#1]#2.south) coordinate (l1)--(l1-|#3) node[midway, above]{#4}}
\newcommand{\action}[3]{\node[draw,thick,fill=white,align=center,below={#1} of {#2}]{#3}}

% Tamarin symbols
\newcommand{\ifarrow}[1][]{\ifthenelse{\equal{#1}{}}{\rightarrow}{-\hspace{-4.22pt}[{#1}]\hspace{-5.6pt}\rightarrow}}
\newcommand{\semarrow}[1][]{\ifthenelse{\equal{#1}{}}{\Rightarrow}{=\hspace{-3.0pt}[{#1}]\hspace{-3pt}\Rightarrow}}
\newcommand{\mIn}{\mathsf{In}}
\newcommand{\mOut}{\mathsf{Out}}
\newcommand{\mFr}{\mathsf{Fr}}
\newcommand{\mKD}{\mathsf{KD}}
\newcommand{\mKU}{\mathsf{KU}}
\newcommand{\mT}[1]{\text{\texttt{#1}}}

\begin{document}
\title{Extended Formal Analysis of the EDHOC Protocol in Tamarin}
\author{
    Karl Norrman\inst{1,2}\orcidID{0000-0003-0164-1478} \and
    Vaishnavi Sundararajan\inst{3}\orcidID{0000-0002-5945-5208} \and
    Alessandro Bruni\inst{4}
}
\authorrunning{Norrman, Sundararajan and Bruni}
\institute{
    KTH Royal Institute of Technology, Stockholm, Sweden \and
    Ericsson Research, Security, Stockholm, Sweden\\
    \email{karl.norrman@ericsson.com} \and
    University of California, Santa Cruz, USA\\
    \email{vasundar@ucsc.edu} \and
    IT University of Copenhagen, Copenhagen, Denmark\\
    \email{brun@itu.dk}
}

@@

%-------------------------------------------------------------------------- sub
\subsection{\mTamarin{}}
\label{sec:tamarin}
We extend the formal model of~\cite{Norr21}, using the tool \mTamarin{}~\cite{DBLP:conf/cav/MeierSCB13}, which is an 
interactive
tool for the symbolic verification of security protocols.
%
Protocols are modelled in \mTamarin{} as multiset rewrite rules which encode 
a
transition relation.
%
The elements of these multisets, called facts, contribute to the global
system state.
%
For syntactic sugar, \mTamarin{} also allows the use of let-bindings and tuples.
%
For ease of presentation, we will present the model and properties in a
slightly different syntax in this paper, but this syntax can be directly
mapped to that of \mTamarin.
%

@@

\begin{figure*}[htp]
\begin{align*}
    \mPredPcs \triangleq\ & \forall \mTID, I, R, \mSessKey, t_2, t_3\mLogicDot
    \mK^{t_3}(\mSessKey)\  \land\ 
    (\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, 
\mRComplete^{t_2}(\mTID, 
I, R, 
\mSessKey))
    \rightarrow\\
    &(\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)
    \ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(R, \mSessKey))
    \ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(I, \mSessKey))\\
	&\ \lor\ (\exists t_0, t_1, Z'\mLogicDot \mIStart^{t_0}(\mTID, I, R, Z') \land 
\mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\
    &\ \lor\ (\exists t_0, t_1, Z'\mLogicDot \mRStart^{t_0}(\mTID, I, R, Z') 
\land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[1em]
%    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID, R, \mSessKey, S) 
%\land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_2\mLogicDot \mIComplete^{t_2}(\mTID_{I}, I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_R, t_1\mLogicDot \mRStart^{t_1}(\mTID_R, R, \mSessKey, 
S) \land t_1 \lessdot t_2
    \land (\forall \mTID_I', I', R', t_1' \mLogicDot \mIComplete^{t_1'}(\mTID_I', 
I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_2))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1, Z'\mLogicDot \mIStart^{t_0}(\mTID_I, I, R, Z') \land 
\mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[1em]
%
    \mPredInjR \triangleq\ &
    \forall \mTID_R, I, R, \mSessKey, S, t_2\mLogicDot 
\mRComplete^{t_2}(\mTID_R, 
I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_I, t_1\mLogicDot \mIStart^{t_1}(\mTID_I, I, R, \mSessKey, 
S) \land t_1 \lessdot t_2
    \land (\forall \mTID_R', I' R' t_1' \mLogicDot 
\mRComplete^{t_1'}(\mTID_R', 
I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_2))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1, Z', S'\mLogicDot \mRStart^{t_0}(\mTID_R, R, 
Z', S') \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot 
t_2))\\[1em]
%
    \mPredImpI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_1\mLogicDot 
\mIComplete^{t_1}(\mTID_I, 
I, R, \mSessKey, 
S)
    \rightarrow\\
      &(\forall \mTID_R, I', R', S', t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, 
I', R', \mSessKey, S') \rightarrow
             (I=I' \land R=R' \land S=S')\\
      &\ \land (\forall \mTID_I', I', R', S', t_1'\mLogicDot
        \mIComplete^{t_1'}(\mTID_I', I', R', \mSessKey, S') \rightarrow t_1' \doteq 
t_1
        ))\\
    &\lor(\exists t_0\mLogicDot \mRevLTK^{t_0}(R) \land t_0 \lessdot t_1)
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey))\\
    &\lor\ (\exists t_0, t_1, Z'\mLogicDot \mIStart^{t_0}(\mTID_I, I, R, Z') \land 
\mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[1em]
%
	\mSecADthree \triangleq\ &
	\forall \mADthree, I, R, \mSessKey, \mTID_{I}, t_{3}, t_{2}\mLogicDot  \mK^{t_{3}}(\mADthree) \land \mISend^{t_{2}}(I, R, \mSessKey, \mADthree, \mTID_{I}) \rightarrow \\
	& ( (\exists t_{1}\mLogicDot \mRevLTK^{t_{1}}(I) \land t_{1} \lessdot t_{2})\lor(\exists t_{1}\mLogicDot \mRevLTK^{t_{1}}(R) \land t_{1} \lessdot t_{2}) \\
	&\ \ \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
     \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey)) \\
    &\ \ \lor(\exists t_{0}, t_{1}, Z'\mLogicDot \mIStart^{t_{0}}(\mTID_{I}, I, R, Z') \land \mTEE^{t_{1}}(R) \land t_{0} \lessdot t_{1}) \\
    &\ \ \lor(\exists t_{0}, t_{1}, t_{4}, \mTID_{R}, Z', S'\mLogicDot \mTEE^{t_{1}}(I) \land \mRRecv^{t_{4}}(I, R, Z, \mADthree, \mTID_{R}) \land \mRStart^{t_{0}}(\mTID_{R}, R, Z', S') \land t_{0} \lessdot t_{1}))\\[1em]
%
	\mIntADthree \triangleq\ &
	\forall \mADthree, I, R, \mSessKey, \mTID_{R}, t_{3}\mLogicDot 
	\mRRecv^{t_{3}}(I, R, \mSessKey, \mADthree, \mTID_{R}) \rightarrow \\
	& ( (\exists \mTID_{I}, t_{2}\mLogicDot \mISend^{t_{2}}(I, R, \mSessKey, \mADthree, \mTID_{I}) \land t_{2} \lessdot t_{3}) \\
	&\ \lor (\exists t_{2}\mLogicDot \mRevLTK^{t_{2}}(I) \land t_{2} \lessdot t_{3}) \lor(\exists t_{2}\mLogicDot \mRevLTK^{t_{2}}(R) \land t_{2} \lessdot t_{3}) \\
	&\ \ \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
     \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey)) \\
     &\ \ \lor(\exists t_{0}, t_{1}, t_{2}, \mTID_{I}, Z'\mLogicDot \mTEE^{t_{1}}(R) \land \mISend^{t_{2}}(I, R, \mSessKey, \mADthree, \mTID_{I}) \land \mIStart^{t_{0}}(\mTID_{I}, I, R, Z') \land t_{0} \lessdot t_{1}) \\
     &\ \ \lor(\exists t_{0}, t_{1}, Z', S'\mLogicDot \mTEE^{t_{1}}(I) \land \mRStart^{t_{0}}(\mTID_{R}, R, Z', S') \land t_{0} \lessdot t_{1})
	)
\end{align*}
\caption{Formalization of security properties}
\label{fig:props}
\end{figure*}

@@

In the \mIComplete{} event, \mTID{} represents a ``thread identifier'' which uniquely identifies the
current session, $I$ represents the identity of the initiator,
and $R$ represents the identity of the party who the initiator believes is
playing the responder role, while \mSessKey{} stands for the established
session-key material.
%
\mRComplete{} has analogous parameters; in particular, the responder $R$
believes $I$ is the party playing the initiator role.
%
Intuitively, the PCS property states that an adversary obtains \mSessKey{}
only if one of the following conditions hold: either a party's long-term key
is compromised before their run ends, or the TEE interface for the responder is used during the current
session for the initiator, i.e., after the initiator starts and before it
completes, or, similarly, the TEE interface for the initiator is used during the
current session for the responder.
%
Note that the properties in Figure~\ref{fig:props} are unlike the actual \mTamarin{} lemma in one minor way: \mTamarin's logic does not allow disjunctions to appear on
the left-hand side of an implication inside a universally-quantified formula.
%
Therefore, in the \mTamarin{} code, instead of using the disjunction
$\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\,
\mRComplete^{t_2}(\mTID, I, R, \mSessKey)$
to model the fact that either party may have completed their execution, we use
a single action parametrized by the terms $\mTID$, $I$, $R$, and \mSessKey.

@@

%---------------------------------------------------------------------------sub
\subsection{Encoding \mEdhoc{} in \mTamarin{}}
\label{sec:modeling}
%
In this section, we describe how we model the \mSigSig, \mSigStat, \mStatSig,
and \mStatStat{} methods of \mEdhoc{} in \mTamarin.
%
As in~\cite{Norr21}, we construct the \mTamarin{} model by utilizing the fact
that all methods of \mEdhoc{} share a common underlying structure
(as shown in Figure~\ref{fig:edhocFramework}).
%
We do so by using a single specification file in the M4 macro language,
which generates all the methods.
%
As in~\cite{Norr21}, we only present the \mStatSig{} method which illustrates
the use of two different authentication methods.
%
The full \mTamarin{} code for all models can be found 
at~\cite{dropboxrepo}.
%

@@

\begin{scriptsize}
\begin{verbatim}
1 lemma secrecyPCS:
2    all-traces
3    "All u v sk tid #t3 #t2.
4       (K(sk)@t3 & CompletedRun(u, v, sk, tid)@t2) ==>
5       ( (Ex #t1. LTKRev(u)@t1 & #t1 < #t2)
6       | (Ex #t1. LTKRev(v)@t1 & #t1 < #t2)
7       | (Ex #t1. EphKeyRev(sk)@t1)
8       | (Ex m1 #t0 #k. I1(tid, u, v, m1)@t0 & TEE(v)@k & (t0 < k | k < t2))
9       | (Ex m1 m2 #t0 #k. R2(tid, v, m1, m2)@t0 & TEE(u)@k & (t0 < k | k < t2))
10    )"
\end{verbatim}
\end{scriptsize}
%
